---
title: "ESM 232 - assignment3"
author: "Claire Madden and Lydia Bleifuss"
date: "4/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(sensitivity)
library(pse)
library(here)


clim_data <- read_csv(here("Data", "clim.csv"))

source("../R/yield_anom.R")
```


```{r parameters}

# considering all parameters in the yield_anom model
factors <- c("tn1", "tn2", "p1", "p2", "int")

# number of parameter sets to run
nsets = 500

# set distributions

q = c("qnorm", "qnorm", "qnorm", "qnorm", "qnorm")



q.arg = list(list(mean = -0.015, sd = abs(0.2*-0.015)),
             list(mean = -0.0046, sd = abs(0.2*-0.0046)),
             list(mean = -0.07, sd= abs(0.2*-0.07)),
             list(mean = 0.0043, sd = abs(0.2*0.0043)),
             list(mean = 0.28, sd = abs(0.2*0.28)))

# unsure if calling each variable by name in function will give us the correct value to calculate sd, so used actual number values instead
```

```{r LHS}


# generate samples from LHS
sens1 <- LHS(NULL, factors, nsets, q, q.arg)

sens_pars <- get.data(sens1)


# create matrix to store results
sens1_results <- matrix(nrow = nsets, ncol = 1)

# read in input data in set up code chunk as 'clim_data'


# notice that MoreArgs is used for inputs that are the same for each set
df_almond = mapply(FUN=yield_anom, 
                   tn1=sens_pars$tn1, 
                   tn2=sens_pars$tn2,
                   p1=sens_pars$p1,
                   p2=sens_pars$p2,
                   int=sens_pars$int,
                   MoreArgs=list(clim_data=clim_data))


# use unlist to get a matrix
sens1_results <- matrix((unlist(df_almond)), ncol=1, byrow=TRUE)

colnames(sens1_results)=c("mean_anom_LHS")


# to take advantage of LHS/pse functions for plotting interesting information we can send results back
sens1 = pse::tell(sens1, t(sens1_results), res.names=c("mean_anom_LHS"))
pse::plotscatter(sens1, col="blue", cex=5) #p2!

pse::plotprcc(sens1) #p2! most sensitive, p1 is next, then tn2, tn1 and then int
sens1$prcc


# we can also plot results in interesting ways
# turn sens1_results into a data frame - easier access to R plotting functions

sens1_LHS = as.data.frame(sens1_results) #bind with sobel later

```


```{r Sobel}

np=500

# generate two examples of random number from parmeter distributions

tn1_s = rnorm(mean = -0.015, sd = abs(0.2*-0.015), n=np)
tn2_s = rnorm(mean = -0.0046, sd = abs(0.2*-0.0046), n=np)
p1_s = rnorm(mean = -0.07, sd= abs(0.2*-0.07), n=np)
p2_s = rnorm(mean = 0.0043, sd = abs(0.2*0.0043), n=np)
int_s = rnorm(mean = 0.28, sd = abs(0.2*0.28), n=np)

# Sample 1

X1 = cbind.data.frame(tn1_s, tn2_s, p1_s, p2_s, int_s)

tn1_s = rnorm(mean = -0.015, sd = abs(0.2*-0.015), n=np)
tn2_s = rnorm(mean = -0.0046, sd = abs(0.2*-0.0046), n=np)
p1_s = rnorm(mean = -0.07, sd= abs(0.2*-0.07), n=np)
p2_s = rnorm(mean = 0.0043, sd = abs(0.2*0.0043), n=np)
int_s = rnorm(mean = 0.28, sd = abs(0.2*0.28), n=np)

# Sample 2

X2 = cbind.data.frame(tn1_s, tn2_s, p1_s, p2_s, int_s)


sens1_sobel = sobol2007(model = NULL, X1, X2, nboot = 100)

# run model for all parameter sets
sens1_results_sobel = mapply(FUN=yield_anom,  
                             tn1=sens1_sobel$X$tn1_s,
                             tn2=sens1_sobel$X$tn2_s,
                             p1=sens1_sobel$X$p1_s, 
                             p2=sens1_sobel$X$p2_s, 
                             int=sens1_sobel$X$int_s,
                             MoreArgs=list(clim_data=clim_data))


sens1_sobel = sensitivity::tell(sens1_sobel,sens1_results_sobel, sens1_results_sobel.names="ga")


# first-order indices (main effect without co-variance)
sens1_sobel$S

# total sensitivity index -note that this partitions the output variance - so values sum to 1
sens1_sobel$T

# The difference between the main effect and total effect can tell us something about how the parameter influences results
# so in the main effect we include interactions with other parameters

print(sens1_sobel)
plot(sens1_sobel)

# compare with LHS and PRCC
sens1$prcc


sens1_sobel$S
sens1_sobel$T

# make a data frame for plotting
sens1_sobel_500 = cbind.data.frame(sens1_sobel$X, anom=sens1_sobel$y)




```

#### Rank the parameters in term of their sensitivity:

in both methods, p2 is the most sensitive parameter
               
in LHS, p1 is also contributing a lot to the variance
               
in sobel p2 is much more sensitive than all the other parameters
```{r Rank}

# in both methods, p2 is the most sensitive parameter
# in LHS, p1 is also contributing a lot to the variance
# in sobel p2 is much more sensitive than all the other parameters

```


Graph uncertainty in mean yield anomaly across all parameter uncertainty (boxplot and cummulative distribution of the output).

```{r Graph 500}

# we can also plot results in interesting ways
# turn sens_results into a data frame - easier access to R plotting functions

lhs_anom <- sens1_LHS %>% 
  mutate(sens_type = "LHS") %>% 
  rename(anom = "mean_anom_LHS")

sobel_anom <- sens1_sobel_500 %>% 
  dplyr::select(anom) %>% 
  mutate(sens_type = "sobel")

sens1_outputs <- rbind(lhs_anom, sobel_anom)

ggplot(data = sens1_outputs, aes(x = sens_type, y = anom))+
  geom_boxplot(aes(fill = sens_type))+
  labs(x = "Sensitivity Analysis Type",
       y = "Variance in Anomaly",
       title = "Variance in Almond Yield Anomaly with 500 sets of \nNormally Distributed Parameter Values",
       fill = "Sensitivity Test")+
  theme_bw()




```



Repeat using twice as many parameter sets as you did in your first sensitivity analysis - and look at how this changes the sensitivity results

```{r Graph 1000}

#LHS

nsets = 1000

# generate samples from LHS
sens1 <- LHS(NULL, factors, nsets, q, q.arg)

sens_pars <- get.data(sens1)


# create matrix to store results
sens1_results <- matrix(nrow = nsets, ncol = 1)

# read in input data in set up code chunk as 'clim_data'


# notice that MoreArgs is used for inputs that are the same for each set
df_almond = mapply(FUN=yield_anom, 
                   tn1=sens_pars$tn1, 
                   tn2=sens_pars$tn2,
                   p1=sens_pars$p1,
                   p2=sens_pars$p2,
                   int=sens_pars$int,
                   MoreArgs=list(clim_data=clim_data))


# use unlist to get a matrix
sens1_results <- matrix((unlist(df_almond)), ncol=1, byrow=TRUE)

colnames(sens1_results)=c("mean_anom_LHS")


# to take advantage of LHS/pse functions for plotting interesting information we can send results back
sens1 = pse::tell(sens1, t(sens1_results), res.names=c("mean_anom_LHS"))
pse::plotscatter(sens1, col="blue", cex=5) #p2!

pse::plotprcc(sens1) #p2! most sensitive, p1 is next, then tn2, tn1 and then int
sens1$prcc


# we can also plot results in interesting ways
# turn sens1_results into a data frame - easier access to R plotting functions

sens1_LHS_1000 = as.data.frame(sens1_results) #bind with sobel later


```


```{r}
# SOBEL

np=1000

# generate two examples of random number from parmeter distributions

tn1_s = rnorm(mean = -0.015, sd = abs(0.2*-0.015), n=np)
tn2_s = rnorm(mean = -0.0046, sd = abs(0.2*-0.0046), n=np)
p1_s = rnorm(mean = -0.07, sd= abs(0.2*-0.07), n=np)
p2_s = rnorm(mean = 0.0043, sd = abs(0.2*0.0043), n=np)
int_s = rnorm(mean = 0.28, sd = abs(0.2*0.28), n=np)

# Sample 1

X1 = cbind.data.frame(tn1_s, tn2_s, p1_s, p2_s, int_s)

tn1_s = rnorm(mean = -0.015, sd = abs(0.2*-0.015), n=np)
tn2_s = rnorm(mean = -0.0046, sd = abs(0.2*-0.0046), n=np)
p1_s = rnorm(mean = -0.07, sd= abs(0.2*-0.07), n=np)
p2_s = rnorm(mean = 0.0043, sd = abs(0.2*0.0043), n=np)
int_s = rnorm(mean = 0.28, sd = abs(0.2*0.28), n=np)

# Sample 2

X2 = cbind.data.frame(tn1_s, tn2_s, p1_s, p2_s, int_s)


sens1_sobel = sobol2007(model = NULL, X1, X2, nboot = 100)

# run model for all parameter sets
sens1_results_sobel = mapply(FUN=yield_anom,  
                             tn1=sens1_sobel$X$tn1_s,
                             tn2=sens1_sobel$X$tn2_s,
                             p1=sens1_sobel$X$p1_s, 
                             p2=sens1_sobel$X$p2_s, 
                             int=sens1_sobel$X$int_s,
                             MoreArgs=list(clim_data=clim_data))


sens1_sobel = sensitivity::tell(sens1_sobel,sens1_results_sobel, sens1_results_sobel.names="ga")


# first-order indices (main effect without co-variance)
sens1_sobel$S

# total sensitivity index -note that this partitions the output variance - so values sum to 1
sens1_sobel$T

# The difference between the main effect and total effect can tell us something about how the parameter influences results
# so in the main effect we include interactions with other parameters

print(sens1_sobel)
plot(sens1_sobel)

# compare with LHS and PRCC
sens1$prcc


sens1_sobel$S
sens1_sobel$T

# make a data frame for plotting
sens1_sobel_1000 = cbind.data.frame(sens1_sobel$X, anom=sens1_sobel$y)



```

```{r graph 1000}


lhs_anom <- sens1_LHS_1000 %>% 
  mutate(sens_type = "LHS") %>% 
  rename(anom = "mean_anom_LHS")

sobel_anom <- sens1_sobel_1000 %>% 
  dplyr::select(anom) %>% 
  mutate(sens_type = "sobel")

sens1_outputs <- rbind(lhs_anom, sobel_anom)

ggplot(data = sens1_outputs, aes(x = sens_type, y = anom))+
  geom_boxplot(aes(fill = sens_type))+
  labs(x = "Sensitivity Analysis Type",
       y = "Variance in Anomaly",
       title = "Variance in Almond Yield Anomaly with 1000 sets of \nNormally Distributed Parameter Values",
       fill = "Sensitivity Test")+
  theme_bw()


```



#### Short write up describing what you learned from the sensitivity analysis

Depending on the type of sensitivity analysis you choose, results may be different. It is important to identify which type of analysis is appropriate to answer the question you are asking. If you think there is the likelihood of covariance between variables, it is better to use the Sobel method. Increasing the number of parameter sets that you produce to test sensitivity can help to reach a more robust output. 

